Installer is an application included in macOS that extracts and installs
files out of \vv{.pkg} packages. When \vv{Installer} pops up a window for
privileged permission during the installation of \vv{jdk-7u80-macosx-x64},
moving the cursor out of the popup window triggers spinning cursor. As we
input the password directly before the round of triggering the spinning cusor,
\xxx gets the baseline scenario for comparison. Examing the \spinningnode
and its \similarnode, \xxx figures out one thread from daemon \vv{authd}
blocks on semaphore. The root cause is the authentication of user's previledge
synchronously in the main thread, instead of the handler for moving cursor. The
result was verified with \vv{lldb}. The main thread blocks in a synchronous
message to \vv{authd} in API \vv{[IFRunnerProxy\ requestKeyForRights:askUser:]}.

We also discovered a communication pattern in \vv{Installer} indicating the
crucial of interactive debugging in \xxx. It involves four vertices in four
threads, vertex $Vertex_{main}$ in the main thread, and $Vertex_1$ to $Vertex_3$
in three worker threads. First, the main thread wakes up three worker threads.
Then one worker thread is scheduled to run. At its end, another worker thread,
which waits on mutex lock, is woken in $Vertex_2$, which in turn wakes up the
next worker thread in $Vertex_3$. While \xxx is slicing backward, $Vertex_3$
has two incoming edges: one is from $Vertex_{main}$, and the other one is from
$Vertex_2$. Since users can peek the edges before making decision, they are
likely to figure out that the three worker threads contend with mutex lock, and
all of them are the heirs of $Vertex_{main}$.
