\subsection{Long Running}

In this section, we discuss the cases where the \spinningnode is busy on the
CPU. Most of the text editing apps fall into this bug category. We studied
TeXstudio, TextEdit, Microsoft Word, Sublime Text, Text Mate and CotEditor to
reveal their root causes.

%represent cases in this category.

\paragraph{3-TeXStudio}

TeXstudio~\cite{texstudio} is an integrated writing environment for creating
LaTeX documents from github. We noticed a user reported spinning cursor when he
modified his bib file. Alhough the issue was closed by the developer, due to
insufficient information to reproduce the bug, we reproduced it with a large bib
file opened in a tab. Each time we touched the file through another editor, vim
for example, the application window showed a spinning cursor.

\xxx figures out the \spinningnode is busy processing. Slicing the path from
the vertex, \xxx reaches the daemon ``\vv{fseventd}'' and figures out that the
long-running function is invoked by a callback function from this daemon. The
advantage of \xxx over other debugging tools is it helps to narrow down the root
cause with the path. If the user's bug report had included details captured with
\xxx, it may have provided the developer with enough information to reproduce
the bug successfully.

\paragraph{6-TextEdit}

TexEdit is a simple word processing and text editing tool shipped by Apple. \xxx
figured out the root cause by automatic slicing, which reveals the same path as
the interactive version.

It is not surprising because the pattern of vetices in the case fits the
hueristics in \xxx, which chooses the most recent incomming edge. We observed
in the vertex that a kernel thread was woken up from the wait on IO by another
kernel thread; and it processed the timer armed by TextEdit and woke up the
TextEdit. The first incoming edge is from the second kernel thread, and the
second incoming edge is from TextEdit, from vertex where the timer armed to the
one it is processed. Humans can make decision on the vertex base on the event
sequence, which implies the story: TextEdit first arms the timer for IO work,
then kernel threads work for it, and finally it processes the timer and wakes up
TextEdit when finished.

Although the automatic heuristics works for the particular simple tool, it is
not general enough to make decision for all patterns on complex softwares.

\paragraph{7-MSWord}

Microsoft Word is a large and complex piece of software. \xxx can analyze the
event graph, but it identifies multiple possible root causes: the length of path
interactively sliced from the \spinningnode is 67, while the automatic slicing
generates a path of 136 vertices.

%We rely on user interactions to help speed up the path slicing.

We compared the path and find that the earliest difference exists in
the predecessor of the third vertex in backward paths. In the vertex,
user can learn from the callstack that Microsoft Word launches a service
NSServiceControllerCopyServiceDictionarie after being woken by another MSWord
thread; this thread then sends a message to \vv{launchd} to register the new
service and waits for a reply message. With the most recent edge heuristics in
automatic slicing, \xxx chose \vv{launchd} as its precedessor, but the user can
more precisely identify that the execution segment is on behalf of the first
thread. We rely on user interaction in this case to find the true root cause,
since \xxx has identified multiple possibilities.

\paragraph{Other Editing Apps}

Select, copy, paste, delete, insert and save are common operations for text
editing. However, these operations on a large context usually trigger spinning
cursors. Depending on their implementations, CotEditor and TextMate successfully
avoid hangs on copy and selection operation. \xxx can helps the developer to
figure out the more efficient way to implement event handlers. We briefly list
the reports from \spinningnode, including the event handler and most costly
functions. We also list corresponding user input event from the path slicing in
Table~\ref{table:texteditapps}.

\begin{table}[H]
\footnotesize
\centering
  \begin{tabularx}{\columnwidth}{l|l|l}
                  &                     &\\
  \textbf{BUG-ID} & \textbf{costly API} &UI\\
  \hline
  \hline
  5-Notes         & \begin{tabular}{@{}l@{}}
  					\vv{1)NSDetectScrollDevices}\\
					\vv{\xspace ThenInvokeOnMainQueue}\\
					\end{tabular}
   		          & \begin{tabular}{@{}l@{}}
				  	\vv{system}\\
					\vv{defined}\\
					\vv{event}
					\end{tabular}
				  \\
  \hline
  6-TexEdit       & \begin{tabular}{@{}l@{}}
  					\vv{1)[NSTextView(NSPasteboard) \_write}\\
					\vv{\xspace RTFDInRanges:toPasteboard:]}\\
					\vv{2)get\_vImage\_converter}\\
  					\vv{3)get\_full\_conversion\_code\_fragment}\\
					\end{tabular}
				  & \vv{key c}
				  \\
  \hline
  7-MSWord        & \begin{tabular}{@{}l@{}}
					\vv{1)-[NSPasteboard setData:}\\
					\vv{\xspace forType:index:usesPboardTypes:]}\\
 					\vv{2)\_CFStringCreateImmutableFunnel3}\\
  					\vv{3)platform\_memmove}\\
					\vv{4)lseek}, \vv{5)fstat64}, \vv{6)fcntl}\\
					\end{tabular}
				  & \vv{key c}
				  \\
  \hline
  8-SlText   & \begin{tabular}{@{}l@{}} 
					\vv{1)px\_copy\_to\_clipboard}\\
  					\vv{2)\_\_CFToUTF8Len}\\
  					\end{tabular}
				  & \vv{key c}
				  \\
  \hline
  9-TextMate      & \begin{tabular}{@{}l@{}}
  					\vv{1)-[OakTextView paste:]}\\
					\vv{2)CFAttributedStringSet}\\
					\vv{3)TASCIIEncoder::Encode}\\
  					\end{tabular}
				  & \vv{key v}
				  \\
  \hline
  10-CotEditor    & \begin{tabular}{@{}l@{}}
  					\vv{1)CFStorageGetValueAtIndex}\\
					\vv{2)-[NSBigMutableString}\\
					\vv{\xspace characterAtIndex:]}\\
  					\end{tabular}
   		          & \begin{tabular}{@{}l@{}}
				  	\vv{key}\\
				  	\vv{Return}
  					\end{tabular}

				  \\
  \hline
  \end{tabularx}
  \caption{Root cause of spinning cursor in editing Apps}
  \label{table:texteditapps}
\end{table}

