\section{Related Work}
\label{sec:related-work}

While there is currently no system that can help users debug performance
issues in closed-source applications on proprietary MacOS, several active
research topics are closely related.

\textbf{Event tracing.}  Magpie~\cite{barham2004using} is perhaps the closest to
our work.  It monitors server applications in Windows with the goal to model
the normal behaviors of a server application in response to a workload.  This
model further helps detecting anomalies statistically.  In contrast, \xxx's
goal is to identify the root causes of performance issues.  Its graphs are not
request graphs, but rather graphs that may contain many requests.  In addition,
it logs normal and abnormal executions in the same event trace.  In addition,
Magpie requires a manual-written event schema for all involved applications to
capture precise request graphs, whereas \xxx has a simple, application-agnostic
schema for system-wide tracing and enables users to provide more
application-specific knowledge on demand.

Panappticon \cite{zhang2013panappticon} monitors a mobile system and uses the
trace to characterize the user transactions of mobile apps.  Although it
aims to track system-wide events and correlate them without developer
input, it supports only two models of communication: work queue and thread
pooling.

AppInsight \cite{ravindranath2012appinsight} instruments application to
identify the critical execution path in a user transaction.  It supports the
event callback pattern, and does not trace across process or app boundaries.

XTrace, Pinpoint and \etc ~\cite{fonseca2007x, chen2002pinpoint,
chow2014mystery} trace the path of a request through a system using a unique
identifier attached to each request and stitch traces together with the
identifier.  \xxx does not assume the presence of a unified identifier in
closed-source, third-party applications, frameworks, and libraries.

Aguilela \cite{aguilera2003performance} uses timing analysis to correlate
messages to recover their input-output relations while treating the application
as a black box.

\textbf{Performance anomaly detection.}  Several systems detect performance
anomalies automatically.  \cite{han2012performance, yuan2012conservative}
leverage the user logs and call stacks to identify the performance anomaly.
\cite{cohen2004correlating, saidi2008full, xu2009detecting, du2017deeplog}apply
the machine learning method to identify the unusual event sequence as an
anomaly.  \cite{yu2014comprehending} generates the wait and waken graph from
sampled call stacks to stidy a case of performance anomaly.

These systems are orthogonal to \xxx as \xxx's goal is to diagnose an
already-detected performance anomaly.  These systems can help \xxx by detecting
more accurately when a performance issue arises.
