Sequel Pro is a fast, easy-to-use Mac database management application for
working with MySQL databases. It allows user to connect to database with a
standard way, socket or ssh. We noticed spinning beachballs while the network
connection was lost and Sequel Pro tried re-connections.

We collect tracing data in two cases: 1) network connected quickly when we
login, and 2) Sequel Pro lost connection for a while. \xxx first identifies the
spinning node from SequelPro's main thread.
%In the node are the event sequence:
%\textit{System\_call(poll), System\_call(write),
%System\_call(wakeup), Timer(re\_arm), System\_call(read), Wait(lock)}.
With the Algorithm FindSimilarNode, \xxx got a baseline node in case 1). From
there, \xxx goes along the weak edge from wait event to wake\_up event to figure
out the node that missing in case 2) and slices path backwards in case 1). \xxx
carries out the comparison of the nodes in the thread before the normal node
gets waken and before the spinning beachball shows up. The close examination
tells that the main thread is waiting for the kernel thread, which in turn waits
for the ssh thread.

\xxx helps to filter out overconnetions by dividing XXX combined batching node
with hueristics, and recovers XXX missing edges due to the shared flag. In the
diagnosis process, we get XXX similar node, XXX times of queries on backward
slicing , XXX nodes for inspect.

%%Such result could hardly figure out by lldb or
%%spindump as both of them only focus on the call stack snapshot for each process,
%%instead of providing the connections based the execution history system wide.
