\subsection{Sequel Pro}

Sequel Pro is a fast, easy-to-use Mac database management application for
working with MySQL databases. It allows user to connect to database with a
standard way, socket or ssh. We noticed spinning beachballs while the network
connection was lost and Sequel Pro tried reconnections. In the worst case, work
in other tabs get lost if the reconnection fails.

We simulate the unstable network environment by randomly disabled the network
for 1 second, and collect data covering the case that network reconnection
successes quickly and the one that Sequel Pro losts connection for a while. 2G
tracing data are stored and the graph we generated contains 3,650,832 edges
and 2,412,236 vertexes.

Argus starts analysis from the spinning node in NSEvent thread of Sequel Pro
and finds the corresponding node in its main UI thead. We notice the executuion
sequence,\textit{poll, write, wakeup, re-arm timer, read}, in the node. Sequel
Pro gets blocked on the read. As a result, Argus goes to search the similar
normal node, which has the same sequence but is not blocked for long.  From the
node, Argus goes along the weak edge to figure out which node wakes it up and
slice path backwards.  Argus carries out the comparison of the nodes in the
thread before the normal node gets waken and before the spinning beachball
shows up. The close examination tells that the main thread is waiting for the
kernel thread, which in turn waits for the ssh thread. Such result could hardly
figure out by lldb or spindump as both of them only focus on the callstack
snapshot for each process, instead of providing the connections based the
execution history system wide.
