\section{Implementation}\label{sec:implementation}

In this section, we discuss how \xxx collects tracing events from both kernel
and libraries.
%, and user interactions which \xxx leverages to ease diagnosis.

\subsection{Event Tracing}

Current macOS supports a system-wide tracing
infrastructure~\cite{linktotracetool}. It by default stores events in memory and
flushes them to screen or disk periodically. \xxx extends this infrastructure
with a file-backed ring buffer to support system-wide tests and avoid
exhausting the disk. The file size is set to 2GB by default, approximately 19
million events (about 5 minutes of normal operations). The size can be adjust by
users to accommodate the desired trace history.

Default tracing points in macOS provide too limited information to enact causal
tracing. We therefore instrument both the kernel~\cite{linkofxnusourcecode} (at
the source level) and key libraries (at the binary level) to gather adequate
data. We instrument the kernel with 1,193 lines of code, and binary-instrument
the following libraries: \vv{libsystem\_kernel.dylib}, \vv{libdispatch.dylib},
\vv{libpthread.dylib}, \vv{CoreFoundation}, \vv{CoreGraphics}, \vv{HIToolbox},
\vv{AppKit} and \vv{QuartzCore} in \nlibchanges different places.

%%Next subsection describes our binary instrumentation tool

\subsection{Instrumentation}

Most libraries and applications are closed-source in macOS. To hook
their functions with techniques such as library preloading are not
applicable for two reasons. First libraries use two-level executable
namespace~\cite{twolayernamespace}. Applications access the original library
with file name. Second \xxx traces APIs in libraries which are referenced by other
libraries. Hence, we implemented a binary instrumentation mechanism that
allows users to add tracing points inside a binary image.

Like Detour~\cite{hunt1999detours}, we statically scan instruction patterns
to decide where the instrumentation performs and enact it at runtime. The
user supplies a sequence of instructions for \xxx to search the locations of
interest in the image, and a trampoline function which overwrites the sequence
of instructions and produces tracing data with API \vv{kdebug\_trace} from
Apple. \xxx generates shell code with the trampoline function to replace the
victimized instructions. All of the trampoline functions are grouped into a new
image with an initialization function that triggers the drop-in replacement.
\xxx configures the image in the following steps to finish the instrumentation:
(1) it re-exports all symbols from the original image, so the original code can
be called like a shared library; (2) it renames the original image and applies
original name to the new one to ensure the modifications are properly loaded;
(3) it invokes the initialization function externally with \vv{dispatch\_once}
when the library loads.

\subsection{Tracing Data Flags} \label{subsec:tcp}

As described in (\S\ref{sec:inaccuracy}), under-connection due to the missing
data dependency requires users' interaction. Users specify that reads and writes
to a given variable should be considered data dependencies. Data flag tracing
is possible through \xxx's binary rewriting, but we also provide a simple
command line tool which uses watchpoint registers to record \dataflagwrite and
\dataflagread events. The tool \vv{\xxx\_wp} takes as input the process ID,
path to the relevant binary image, and the symbol name of the global variable.
%Here is a simple example of how a user asks \xxx to trace \vv{\_gOutMsgPending}:

\begin{lstlisting}[language=c++,numbers=none]
\xxx_wp <pid> <binary image path> <symbol name>
\end{lstlisting}

\noindent It first gets symbol's offset in file from the image, and find
its memory address in the process. \xxx injects the watchpoint handler
into \vv{CoreFoundation} with our binary instrumentation mentioned above.
\vv{CoreFoundation} is a fundamental framework for all GUI apps, so the watch
pointer handler can be loaded into the memory space of the target process. The
handler invokes Apple's API \vv{kdebug\_trace} to record the value of the data
flag and its operation type (read or write).

\subsection{Tracing Instructions and Calls}

Users may need to gather more information, such as individual instructions and
call stacks, to come up with and verify a binary patch. \xxx integrates with
\vv{lldb scripts} to capture this information and add it to the corresponding
vertices in the event graph. Our \vv{lldb scripts} gather call stacks at
relevant locations and parameters tainted by user inputs. To reduce the data
collection overhead, only at each beginning of a function call does the script
record a full call stack. While \vv{lldb} steps into functions from apps and
frameworks to record parameters tainted, it steps over and only records the
return value of APIs from low-level libraries (i.e. those with the filename
extension \vv{.dylib}).

The combination of instruction-level tracing and occasional call-stacks offers
more than enough detail to diagnose even the most arcane issues, and in our
experience has been very helpful in multiple steps of an \xxx diagnosis.
