\section{Handling Inaccuracies in Causal Tracing}\label{sec:inaccuracy}

\subsection{Inherent Inaccuracies}
\input{patternfigure}

As explained in \S\ref{sec:background}, causal tracing builds a graph to connect
execution segments on behalf of a request that spread across separate threads
and processes. Based on our experience of building a causal tracing system on
commercial closed-source macOS, we believe such graphs are inherently inaccurate
and contain both \emph{over-connections} which do not really map to
causality, and \emph{under-connections}, missing edges between two vertices
with one causally influencing the other. In this section, we present several
inherently inaccurate patterns we observed and their examples.

\subsubsection{Over Connections} \label{subsec:overconnections}

Over connections usually occur when (1) intra-thread boundaries are missing due
to unknown batch processing programming paradigms or (2) superfluous wake-ups
that do not always imply causality.

\paragraph{Dispatch message batching}

While traditional causal tracing assumes the entire execution of a callback
function is on behalf of one request, we found some daemons implement their
service loop inside the callback function and create false dependencies. In the
code snippet in Figure~\ref{fig:dispatchmessagebatching} from the \vv{fontd}
daemon , function \vv{dispatch\_client\_callout} is installed as a callback to
a work from dispatch queue. It subsequently calls \vv{dispatch\_mig\_server()}
which runs the typical server loop and handles messages from different apps. Any
application or daemon can implement its own server loop this way, which makes it
fundamentally difficult to automatically infer event handling boundaries.

\paragraph{Batching in event processing}

Message activities inside a system call are assumed to be related traditionally.
However, to presumably save on kernel boundary crossings, WindowServer MacOS
system daemon uses a single system call to receive data and send data for
an unrelated event from different processed in its event loop in Figure
~\ref{fig:batchingineventprocessing}. This batch processing artificially makes
many events appear dependent.

\paragraph{Mutual exclusion}

In a typical implementation of mutual exclusion, a thread's unlock operation
wakes up a thread waiting in lock. Such a wake-up may be, but is not always,
intended as causality. However, without knowing the developer intent, any
wake-up is typically treated as causality. 

\subsubsection{Under Connections}\label{subsec:underconnections}

We observe that under connections mostly result from missing data
dependencies.  This pattern is more general than shared-memory flags in ad
hoc synchronization~\cite{xiong2010ad} because it occurs even within a
single thread. 

\paragraph{Data dependency in event processing}
The code for Batching in event processing above also illustrates a causal
linkage caused by data dependency in one thread. WindowServer saves the reply
message in variable \vv{\_gOutMsg} inside function \vv{CGXPostReplyMessage}.
When it calls \vv{CGXRunOneServicePass}, it sends out \vv{\_gOutMsg} if there is
any pending message.

\paragraph{CoreAnimation shared flags}
As shown in the code snippet Figure~\ref{fig:casharedflag}, worker thread can set a
field \vv{need\_display} inside a CoreAnimation object whenever the object needs
to be repainted. The main thread iterates over all animation objects and reads
this flag, rendering any such object. This shared-memory communication creates
a dependency between the main thread and the worker so accesses to these field
flags need to be tracked.

%%However, since each object has such a field flag, \xxx cannot afford to monitor
%%each using a watch point register. Instead, it uses instrumentation to modify
%%the CoreAnimation library to trace events on these flags.

\paragraph{Spinning cursor shared flag}
The very fact that spinning cursors are displayed involves data
flags. Each application contains an \vv{NSEvent} thread which fetches
\vv{CoreGraphics} events from the \vv{WindowServer} daemon, converts them
to \vv{NSApp} events to dispatch to the application's main thread, sets
flag \vv{sCGEventIsDispatchToMainThread} as shown in
Figure~\ref{fig:spinningcursorsharedflags}, and arms a timer to monitor
the processing times of the main thread.  If any \vv{NSApp} event takes
longer than two seconds to process, the main thread will not clear flag
\vv{sCGEventIsDispatchToMainThread}.  When the timer in \vv{NSEvent}
fires, it sets flag \vv{sCGEventIsMainThreadSpinning} and invokes
\vv{WindowServer} to display a spinning cursor.  An interesting fact is
that accesses to these shared-memory flags are controlled via a lock --
the lock is used for mutual exclusion, and does not imply a happens before
relationship.
