\section{Introduction} \label{sec:intro}

Today's web and desktop applications are predominantly parallel or
distributed, making performance issues in them extremely difficult to
diagnose because the handling of an external request is often spread across
many threads, processes, and asynchronous contexts instead of in one
sequential execution segment~\cite{harter2012file}. To manually reconstruct
this graph of execution segments for debugging, developers have to sift
through a massive amount of log entries and potentially code of related
application components~\cite{chen2002pinpoint, zhao2016non, xu2009detecting,
nagaraj2012structured, yuan2012conservative}. More often than not, developers
give up and resort to guessing the root cause, producing ``fixes'' that
sometimes make the matter worse. For instance, a bug in the Chrome browser
engine causes a spinning (busy) cursor in macOS when a user switches the input
method~\cite{chromiumbugreport}. It was first reported in 2012, and developers
attempted to add timeouts to work around the issue. Unfortunately, the bug has
remained open for seven years and the timeouts obscured diagnosis further.

Prior work proposed what we call \emph{Causal tracing}, a powerful technique to
construct request graphs automatically~\cite{reynolds2006pip, fonseca2007x,
benjamin2010dapper, zhang2013panappticon, ravindranath2012appinsight}.  It does
so by inferring (1) the beginning and ending boundaries of the execution
segments (vertices in the graph) involved in handling a request; and (2) the
causality between the segments (edges)---how a segment causes others to do
additional handling of the request. Those causal tracing systems all assumed
certain programming idioms to automate inference. For instance, if a segment
sends a message, signals a condition variable, or posts a task to a work queue,
it wakes up additional execution segments, and prior systems assume that
wake-ups reflect causality. Similarly, they assume that the execution segment
from the beginning of a callback invocation to the end is entirely for handling
the request that causes the callback to be installed.  Compared to debuggers
such as \spindump that capture only the current system state, causal tracing is
quite effective at aiding developers to understand complex causal behaviors and
pinpoint real-world performance issues.

Unfortunately, based on our own study and experience of building a causal
tracing system for the commercial operating system, macOS, we found that modern
applications frequently violate these assumptions. Hence, the request graphs
computed by causal tracing are inaccurate in several ways. First, an inferred
segment may be larger than the actual event handling segment due to batch
processing. Specifically, for performance, an application or its underlying
frameworks may bundle together work on behalf of multiple requests with no clear
distinguishing boundaries. For instance, WindowServer in macOS sends a reply
for a previous request and receives a message for the current request using one
system call \vv{mach\_msg\_overwrite\_trap}, presumably to reduce user-kernel
crossings.

Second, the graphs may be missing numerous causal edges. For instance, consider
data dependencies in which the code sets a flag (\eg, ``\vv{need\_display} = 1''
in macOS animation rendering) and later queries the flag to process a request
further. This pattern is broader than ad hoc synchronization~\cite{xiong2010ad}
because data dependency occurs even within a single thread (such as the buffer
holding the reply in the preceding WindowServer example). Although the number of
these flags may be small, they often express critical causality, and not tracing
them would lead to many missing edges in the request graph. However, without
knowing where the flags reside in memory, a tool would have to trace all memory
operations, incurring prohibitive overhead and adding many superfluous edges to
the request graph.

Third, in any case, many inferred edges may be superfluous because wake-ups do
not necessarily reflect causality. Consider an \vv{unlock()} operation waking up
an thread waiting in \vv{lock()}. This wake-up may be just a happens-stance and
the developer intent is only mutual exclusion. However, the actual semantics of
the code may also enforce a causal order between the two operations.

We believe that, without detailed understanding of application semantics,
request graphs computed by causal tracing are \emph{inherently} inaccurate
and both over- and under-approximate reality. Although developer annotations
can help improve precision~\cite{reynolds2006pip, fonseca2007x}, modern
applications use more and more third-party libraries whose source code is not
available. In the case of tech-savvy users debugging performance issues such
as a spinning cursor on her own laptop, the application's code is often not
available. Given the frequent use of custom synchronizations, work queues, and
data flags in modern applications, it is hopeless to count on manual annotations
to ensure accurate capture of request graphs.

In this work, we present \xxx, an interactive system for debugging performance
issues in modern desktop applications despite the inaccuracy of causal tracing.
\xxx does not construct a per-request causal graph which requires extremely
accurate causal tracing. Instead, it calculates an event graph for a duration
of the system execution to aid diagnosis, and tracks root cause reversely via
both true causality edges as well as weak ones.  Specifically, during causal
path tracking, it keeps humans in the loop, as a debugger should rightly do.
\xxx queries users a judicially few times to (1) resolve a few inaccurate edges
that represent false dependencies and (2) identify potential data flags. 

\xxx represents a dramatically different approach in the design space of causal
tracing, It enables users to provide necessary schematic information on demand,
as opposed to full manual schema upfront for all involved applications and
daemons~\cite{barham2004using, reynolds2006pip, fonseca2007x}. We implemented
\xxx in macOS, a widely used commercial operating system. macOS is
closed-source, as are its common frameworks and many of its applications.  This
environment therefore provides a true test of \xxx. We address multiple nuances
of macOS that complicate causal tracing, and built a system-wide, low-overhead,
always-on tracer. \xxx enables users to optionally increase the granularity of
tracing (\eg, logging call stacks and instruction streams) by integrating with
existing debuggers such as \vv{lldb}.

We evaluated \xxx on \nbug real-world, open spinning-cursor issues in widely
used applications such as the Chromium browser engine and macOS System
Preferences, Installer, and Notes. The root causes of all \nbug issues were
previously unknown to us and, to a large extent, the public. Our results show
that \xxx is effective: it helped us non-developers of the applications find all
root causes of the issues, including the Chromium issue that remained open for
seven years. \xxx mostly needs only less than 3 user queries per issue but they are
crucial in aiding diagnosis. \xxx is also fast: its systems-wide tracing incurs
only \cpuoverhead CPU overhead overall.

%% consider adding comparison to prior approaches
%% Our techniques effectively removed false and added missing edges in the
%% event graph.  Even with our techniques, the resultant graph remain too
%% inaccurate for traditional causal tracing, but, fortunately, an average
%% of XXX user queries suffice to locate the root causes accurately.

%%This paper makes the following contributions: our conceptual realization that
%%causal tracing is inherently inaccurate and that interactive causal tracing is
%%superior than prior work in debugging performance issues in modern applications;
%%our system \xxx that performs system-wide tracing in macOS with little overhead
%%and handles several macOS trickeries that complicate causal tracing; and our
%%results diagnosing real-world spinning cursors and finding root causes for
%%performance issues that have remained open for several years.

This paper is organized as follows. In Section~\ref{sec:overview}, we present
an overview of using \xxx and a Chromium example.
We presents inherently inaccuracy patterns observed in macOS in Section
~\ref{sec:inaccuracy}.
Section~\ref{sec:graphcomputing} describes our event graph from causal tracing,
and Section~\ref{sec:implementation} describes our
tracing implementation and tools for user interaction.
In Section~\ref{sec:casestudy} we present other case
studies, and Section~\ref{sec:evaluation} contains performance evaluation.
We summarize related work in Section~\ref{sec:related-work}, and end with
conclusion in Section ~\ref{sec:conclusion}.
